---
title: "HW2 Statistical Computing"
author: "John Rothen"
date: "9/12/2020"
output: pdf_document
---

## System Settings
Windows 10, 64bit, Rstudio


## Initial Notes

R and Miktex were updated to the most recent versions to avoid any issues.

The repository was then cloned to the local disk using Gitbash command.

$ git clone /repository link/

Rtools was then downloaded, as it is required for many of the packages necessary. The "make" problem was resolved using the following R code:
```
writeLines('PATH="${RTOOLS40_HOME}\\usr\\bin;${PATH}"', con = "~/.Renviron")
```



## Issue 1: package installations,

```{r warning=FALSE}
#install.packages("bookdown")
#install.packages("tinytex")
#install.packages("sloop")
#install.packages("dplyr")
#install.packages("sessioninfo")
#install.packages("lobstr")
#install.packages("DBI")
#install.packages("RSQLite")
#install.packages("jsonlite")
#install.packages("zeallot")
#install.packages("dbplyr")
#install.packages("profvis")
#install.packages("bench")
#install.packages("tidyr")
#install.packages("ggbeeswarm")
library(bookdown)
library(sloop)
library(tinytex)
library(dplyr)
library(sessioninfo)
library(lobstr)
library(DBI)
library(base)
library(RSQLite)
library(jsonlite)
library(knitr)
library(roxygen2)
library(zeallot)
library(dbplyr)
library(profvis)
library(bench)
library(tidyr)
library(ggbeeswarm)
```


# Issue with "emo"

In order to properly display emojis, the dependencies were installed from github.

```{r message=FALSE, warning=FALSE}
#install.packages("devtools")
library(devtools)
#devtools::install_github("hadley/emo")
#devtools::install_github("hadley/sloop")
library(emo)
library(usethis)
library(sloop)
```

# Tinytex issues

Installed tinytex so that the book can be compiled correctly.

```{r}
#install_tinytex()
#devtools::install_github('yihui/tinytex')
options(tinytex.verbose=TRUE)

```

# Missing Fonts

Two fonts are necessary in order to compile, these are Inconsolata and AndaleMono. Once these are added to your tinytex, the compilation should work!

```{}
bookdown::render_book("index.Rmd", output_format = "bookdown::pdf_book")
```

